|

### 2024-10-24 output/seminar-slideshow.qmd
Add color palette

```{r libraries}
library(tibble)
library(dplyr, warn.conflicts = FALSE)
library(knitr)
```

>>>>

```{r libraries}
library(tibble)
library(dplyr, warn.conflicts = FALSE)
library(knitr)
```{r color-palettes}
PALETTE_UNED <- c(
  normal = "#00533e",
  medium = "#427562",
  light  = "#86a699",
  white  = "#cddad5"
)
PALETTE_APPLE <- c(
  normal = "#749f4c",
  medium = "#8aac5d",
  light  = "#a2bc7e",
  white  = "#cddbb8"
)
PALETTE_BLUE <- c(
  normal = "#5c6eb1",
  medium = "#7683bd",
  light  = "#929acb",
  white  = "#d4d6eb"
)
PALETTE_TANGERINE <- c(
  normal = "#d76f47",
  medium = "#dd8964",
  light  = "#e4a482",
  white  = "#f0cfb9"
)
PALETTE_STRAWBERRY <- c(
  normal = "#da5268",
  medium = "#c87384",
  light  = "#daa6b1",
  white  = "#efdbdf"
)
PALETTE_RASPBERRY <- c(
  normal = "#90214a",
  medium = "#8e4d60",
  light  = "#af848b",
  white  = "#dac7c7"
)
```

```
